---
title: "Pretty Doc is Awesome"
author: "Christian Julca"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Summary

I explore [**pressure dataset**](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/pressure.html) available in Rstudio using the `html_pretty` output format in package
[**prettydoc**](http://github.com/yixuan/prettydoc/) , an alternative
to `html_document` and `html_vignette` contained in the `rmarkdown` package,
is able to generate small and nice HTML pages.

# Pressure Dataset Features
Using inline code is possible extract features of dataset:

* `r nrow(pressure)` observations.
* `r length(names(pressure))` variables: `r names(pressure)[1]` and `r names(pressure)[2]`
* Both variables are `r class(pressure$pressure)`
* `r names(pressure)[1]` has `r sum(is.na(pressure$temperature))` missing values
* `r names(pressure)[2]` has `r sum(is.na(pressure$pressure))` missing values


# Plotting Pressure and Temperature

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your package vignette.

```{r fig.width=6, fig.height=6, fig.align='center'}
library(ggplot2)
ggplot(pressure,aes(x=temperature, y=pressure))+
  geom_point(size=3)
```

## Table
Top 6 rows cars dataset
```{r}
library(knitr)
kable(head(cars,6))
```

